---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statxplore

<!-- badges: start -->
<!-- badges: end -->

The statxplore r package acts as a wrapper around DWP's statXplore API for published statistics on benefits, pensions and other areas.

## Installation

The package is not yet available on CRAN, you can install the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("piersyork/statxplore")
```

## Example
To search for available data, you can use `available_databases()` to see which benefits have data available. `available_datasets()` then provides a breakdown of available data for the benefit. `available_fields()` provides the variable names (measure and fields) used to make a query.

```{r search, eval=FALSE}
library(statxplore)

set_api_key("your_api_key") # available in your statXplore account settings

available_databases() # return available databases (topic areas) 

available_datasets(database = "Personal Independence Payment") # what datasets are available for the database

available_fields(database = "Personal Independence Payment", dataset = "PIP Registrations") # what are the avilable measure and fileds

```


Using results from the search, here is an example of how to get data on the number of PIP Registrations per month by age

```{r example, eval=FALSE}

pip_regs_age <- start_query(database = "Personal Independence Payment", dataset = "PIP Registrations") |>
  add_measure("PIP Registrations") |>
  add_fields(c("Month", "Age (bands and single year)")) |>
  fetch()

```

## TO-DO
- [ ] Add caching of data
- [x] Add secure storing of APIKey 
- [ ] Add reading APIKey from file
- [ ] Change method of renaming column names to named vector
- [ ] Fix ordering of column names

